Rclean: A Tool for Writing Cleaner, More Transparent Code

### 2020-02-06 joss/paper.Rmd
Read through and spellcheck

More often then not, when someone is writing an R script, the intent
to produce a set of results, such as a statistical analysis, figure,
table, etc. This set of results is always a subset of a much larger
set of possible ways to explore a dataset, as there are many
statistical approaches and tests, let alone ways to create
visualizations and other representations of patterns in data. This
commonly leads to lengthy, complicated scripts from which researchers
manually subset results, but never refactor, i.e. refine code so that
it is shorter and focused on a desired product.

The goal of `Rclean` is to provide a set of tools that help someone
reduce and organize code based on results. The package uses an
automated technique based on data provenance (details below) to
analyze existing scripts and provide ways to identify and extract code
to produce a desired output. To keep the process simple and
straight-forward much of this process has been abstracted for the
user, and the API has been kept to a minimum set of functions that
enable a user to conduct the following basic workflow:

@@

To conclude, we hope that `Rclean` makes writing scientific software
easier for the R community. We look forward to feedback and help with
extending its application, particularly in the area of
reproducibility, such as using code cleaning in the creation of more
robust capsules [@Pasquier2018]. To get involved, report bugs, suggest
features, please visit the project page.

>>>>

The goal of `Rclean` is to provide a set of tools that help someone
reduce and organize code based on results. More often then not, when
someone is writing an R script, the intent is to produce a set of
results, such as a statistical analysis, figure, table, etc. This set
of results is always a subset of a much larger set of possible ways to
explore a dataset, as there are many statistical approaches and tests,
let alone ways to create visualizations and other representations of
patterns in data. This commonly leads to lengthy, complicated scripts
from which researchers manually subset results, but likely never to be
refactored because of the difficulty in disentangling the code needed
to produce some results and not others. The 'Rclean' package uses an
automated technique based on data provenance (details below) to
analyze existing scripts and provide ways to identify and extract code
to produce a desired output.

To keep the process simple and
straight-forward much of this process has been abstracted for the
user, and the API has been kept to a minimum set of functions that
enable a user to conduct the following basic workflow:

@@

To conclude, we hope that `Rclean` makes writing scientific software
easier for the R community. We look forward to feedback and help with
extending its application, particularly in the area of
reproducibility. To get involved, report bugs, suggest features,
please visit the project page.
